### 2024-03-07 docs/projects/visual-tools/clay-calva-demo-20231216/index.qmd
Clay, Calva, & Noj - rerendered

---
<style></style><style>.printedClojure .sourceCode {
  background-color: transparent;
  border-style: none;
}
</style>
<script src="index_files/md-default1.js" type="text/javascript"></script><script src="index_files/md-default2.js" type="text/javascript"></script><script src="index_files/vega3.js" type="text/javascript"></script><script src="index_files/vega4.js" type="text/javascript"></script><script src="index_files/vega5.js" type="text/javascript"></script>
<div style="max-height:600px;overflow-y:auto;"><table><tr><td>This is part of the Scicloj <a href="https://scicloj.github.io/clojure-data-scrapbook/">Clojure Data Scrapbook</a>.</td><a href="https://scicloj.github.io/clojure-data-scrapbook/"><img align="left" alt="SciCloj logo" src="https://scicloj.github.io/sci-cloj-logo-transparent.png" width="40" /></a></tr></table></div>

@@

::: {.sourceClojure}
```clojure
(ns index
  (:require [scicloj.noj.v1.datasets
             :as datasets]
            [scicloj.noj.v1.vis.hanami
             :as hanami]
            [scicloj.kindly.v4.kind
             :as kind]))
```
:::

@@

<div style="max-height:600px;overflow-y:auto;"><iframe allowfullscreen="allowfullscreen" src="https://www.youtube.com/embed/X_SsjhmG5Ok"></iframe></div>

@@

::: {.sourceClojure}
```clojure
datasets/iris
```
:::

@@

| :sepal-length | :sepal-width | :petal-length | :petal-width |  :species |
|--------------:|-------------:|--------------:|-------------:|-----------|
|           5.1 |          3.5 |           1.4 |          0.2 |    setosa |
|           4.9 |          3.0 |           1.4 |          0.2 |    setosa |
|           4.7 |          3.2 |           1.3 |          0.2 |    setosa |
|           4.6 |          3.1 |           1.5 |          0.2 |    setosa |
|           5.0 |          3.6 |           1.4 |          0.2 |    setosa |
|           5.4 |          3.9 |           1.7 |          0.4 |    setosa |
|           4.6 |          3.4 |           1.4 |          0.3 |    setosa |
|           5.0 |          3.4 |           1.5 |          0.2 |    setosa |
|           4.4 |          2.9 |           1.4 |          0.2 |    setosa |
|           4.9 |          3.1 |           1.5 |          0.1 |    setosa |
|           ... |          ... |           ... |          ... |       ... |
|           6.9 |          3.1 |           5.4 |          2.1 | virginica |
|           6.7 |          3.1 |           5.6 |          2.4 | virginica |
|           6.9 |          3.1 |           5.1 |          2.3 | virginica |
|           5.8 |          2.7 |           5.1 |          1.9 | virginica |
|           6.8 |          3.2 |           5.9 |          2.3 | virginica |
|           6.7 |          3.3 |           5.7 |          2.5 | virginica |
|           6.7 |          3.0 |           5.2 |          2.3 | virginica |
|           6.3 |          2.5 |           5.0 |          1.9 | virginica |
|           6.5 |          3.0 |           5.2 |          2.0 | virginica |
|           6.2 |          3.4 |           5.4 |          2.3 | virginica |
|           5.9 |          3.0 |           5.1 |          1.8 | virginica |

@@

::: {.sourceClojure}
```clojure
(-> datasets/iris
    kind/table)
```
:::

>>>>

---
<style></style><style>.printedClojure .sourceCode {
  background-color: transparent;
  border-style: none;
}
</style>
<script src="index_files/md-default1.js" type="text/javascript"></script><script src="index_files/md-default2.js" type="text/javascript"></script><script src="index_files/vega3.js" type="text/javascript"></script><script src="index_files/vega4.js" type="text/javascript"></script><script src="index_files/vega5.js" type="text/javascript"></script>

```{=html}
<table><tr><td>This is part of the Scicloj <a href="https://scicloj.github.io/clojure-data-scrapbook/">Clojure Data Scrapbook</a>.</td><a href="https://scicloj.github.io/clojure-data-scrapbook/"><img align="left" alt="SciCloj logo" src="https://scicloj.github.io/sci-cloj-logo-transparent.png" width="40" /></a></tr></table>
```

@@

::: {.sourceClojure}
```clojure
(ns index
  (:require [scicloj.metamorph.ml.toydata
             :as toydata]
            [scicloj.noj.v1.vis.hanami
             :as hanami]
            [scicloj.kindly.v4.kind
             :as kind]))
```
:::

@@

```{=html}
<iframe allowfullscreen="allowfullscreen" src="https://www.youtube.com/embed/X_SsjhmG5Ok"></iframe>
```

@@

::: {.sourceClojure}
```clojure
(def iris
  (toydata/iris-ds))
```
:::

::: {.sourceClojure}
```clojure
iris
```
:::

@@

| :sepal_length | :sepal_width | :petal_length | :petal_width | :species |
|--------------:|-------------:|--------------:|-------------:|---------:|
|           5.1 |          3.5 |           1.4 |          0.2 |        0 |
|           4.9 |          3.0 |           1.4 |          0.2 |        0 |
|           4.7 |          3.2 |           1.3 |          0.2 |        0 |
|           4.6 |          3.1 |           1.5 |          0.2 |        0 |
|           5.0 |          3.6 |           1.4 |          0.2 |        0 |
|           5.4 |          3.9 |           1.7 |          0.4 |        0 |
|           4.6 |          3.4 |           1.4 |          0.3 |        0 |
|           5.0 |          3.4 |           1.5 |          0.2 |        0 |
|           4.4 |          2.9 |           1.4 |          0.2 |        0 |
|           4.9 |          3.1 |           1.5 |          0.1 |        0 |
|           ... |          ... |           ... |          ... |      ... |
|           6.9 |          3.1 |           5.4 |          2.1 |        1 |
|           6.7 |          3.1 |           5.6 |          2.4 |        1 |
|           6.9 |          3.1 |           5.1 |          2.3 |        1 |
|           5.8 |          2.7 |           5.1 |          1.9 |        1 |
|           6.8 |          3.2 |           5.9 |          2.3 |        1 |
|           6.7 |          3.3 |           5.7 |          2.5 |        1 |
|           6.7 |          3.0 |           5.2 |          2.3 |        1 |
|           6.3 |          2.5 |           5.0 |          1.9 |        1 |
|           6.5 |          3.0 |           5.2 |          2.0 |        1 |
|           6.2 |          3.4 |           5.4 |          2.3 |        1 |
|           5.9 |          3.0 |           5.1 |          1.8 |        1 |

@@

::: {.sourceClojure}
```clojure
(-> iris
    (kind/table {:element/max-height "500px"}))
```
:::

```{=html}
